### 2022-10-13 types.tex
wip

@@

    {\inferrule{A : in(dₐ : τₐ), A : out(dₐ | τₐ),… ;. : ⊤ ⊢ p : τ}{⊢ "declare"~A…~"in"~p : τ}}

@@

    {\inferrule[relevant-parallel]{C₁;d[n] : τ ⊢ p₁ : τ₁ \\ C₂;d[n+1] :^r τ ⊢ p₂ : τ₂}{C₁,C₂;d[n] :^r τ ⊢ (p₁ ∣ p₂) : (τ₁ ∣ τ₂)}}

    {\inferrule[substructural-fallback]{C;d : τ' ⊢ p : τ}{C;d : τ' ⊢^r p : τ}}

    {\inferrule[general-parallel]{C₁;. : ⊤ ⊢ p₁ : τ₁ \\ C₂;. : ⊤ ⊢ p₂ : τ₂}{C₁,C₂; . : ⊤ ⊢ (p₁ ∣ p₂) : (τ₁ ∣ τ₂)}}

    {\inferrule[exchange]{A : (dₐ : τₐ),  B : (d_b | τ_b) ; d : τ ⊢ p : τ}{B : (d_b | τ_b), A : (dₐ : τₐ) ⊢ p : τ}}

>>>>

\abstract{Adding properties to hydroflow is important, because it
  allows us to do three things: (1) it lets us explicitly state and
  verify the requirements individual hydroflow operators have assumed
  of their inputs in order to be correct, (2) It allows us to encode
  translational goals and optimization correctness conditions, and (3) }

\section{technical todo}

\begin{itemize}
\item Type system: basic structure and derivations ✓
\item Type system: properties and their satisfaction
\item semantics: core semantic model (is it rewrite-based?)
\item Type system: axiom rewrite system
\item core language: axiom extensibility
\item proof: progress+preservation (or its equivalent in axiomatic semantics)
\item proof: axiom admissibility (via bisimulation?)
\item evaluation: example programs which satisfy the above
\item evaluation: programmability assessment
\item evaluation: extensibility assessment (new operators)
\end{itemize}

@@

    {\inferrule{A : in(dₐ : τₐ), A : out(dₐ | τₐ),… ;. : ⊤ ⊢ p : τ}
      {⊢ "declare"~A…~"in"~p : τ}}

@@

    {\inferrule[relevant-parallel]
      {C₁;d[n] : τ ⊢ p₁ : τ₁ \\ C₂;d[n+1] :^r τ ⊢ p₂ : τ₂}
      {C₁,C₂;d[n] :^r τ ⊢ (p₁ ∣ p₂) : (τ₁ ∣ τ₂)}}

    {\inferrule[substructural-fallback]
      {C;d : τ' ⊢ p : τ}
      {C;d : τ' ⊢^r p : τ}}

    {\inferrule[general-parallel]
      {C₁;. : ⊤ ⊢ p₁ : τ₁ \\ C₂;. : ⊤ ⊢ p₂ : τ₂}
      {C₁,C₂; . : ⊤ ⊢ (p₁ ∣ p₂) : (τ₁ ∣ τ₂)}}

    {\inferrule[exchange]
      {A : (dₐ : τₐ),  B : (d_b | τ_b) ; d : τ ⊢ p : τ}
      {B : (d_b | τ_b), A : (dₐ : τₐ) ⊢ p : τ}}
